COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries: Replication Code

### 2021-06-22 paper_files/figure-latex/fig2paper-1.tex
update

% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:30
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

@@

\usepackage[active,tightpage,psfixbb]{preview}

@@

\setlength\PreviewBorder{0pt}
\begin{document}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (722.70,542.02);
\end{scope}
\begin{scope}
\path[clip] ( 78.32, 67.14) rectangle (137.25,464.78);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 78.32, 67.14) rectangle (137.25,464.78);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 87.69, 67.14) --
	( 87.69,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (101.09, 67.14) --
	(101.09,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (114.48, 67.14) --
	(114.48,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (127.88, 67.14) --
	(127.88,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32, 83.94) --
	(137.25, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,111.94) --
	(137.25,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,139.95) --
	(137.25,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,167.95) --
	(137.25,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,195.95) --
	(137.25,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,223.96) --
	(137.25,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,251.96) --
	(137.25,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,279.96) --
	(137.25,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,307.96) --
	(137.25,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,335.97) --
	(137.25,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,363.97) --
	(137.25,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,391.97) --
	(137.25,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,419.98) --
	(137.25,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,447.98) --
	(137.25,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.00, 67.14) --
	( 81.00,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.39, 67.14) --
	( 94.39,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.79, 67.14) --
	(107.79,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (121.18, 67.14) --
	(121.18,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (134.58, 67.14) --
	(134.58,464.78);
\definecolor{drawColor}{RGB}{204,102,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.16,137.15) --
	(111.16,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.16,139.95) --
	( 94.55,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.55,137.15) --
	( 94.55,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (105.80,445.18) --
	(105.80,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (105.80,447.98) --
	(100.02,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.02,445.18) --
	(100.02,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.14,417.18) --
	(101.14,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.14,419.98) --
	( 94.07,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.07,417.18) --
	( 94.07,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.75,361.17) --
	( 90.75,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.75,363.97) --
	( 81.16,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.16,361.17) --
	( 81.16,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.66,333.17) --
	( 94.66,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.66,335.97) --
	( 90.37,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.37,333.17) --
	( 90.37,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 97.50,305.16) --
	( 97.50,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 97.50,307.96) --
	( 89.09,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.09,305.16) --
	( 89.09,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.57,109.14) --
	(101.57,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.57,111.94) --
	( 99.86,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.86,109.14) --
	( 99.86,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.95,277.16) --
	(107.95,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.95,279.96) --
	( 95.41,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.41,277.16) --
	( 95.41,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.09,249.16) --
	(113.09,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.09,251.96) --
	(106.23,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (106.23,249.16) --
	(106.23,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.20,221.16) --
	(116.20,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.20,223.96) --
	(107.84,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.84,221.16) --
	(107.84,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.00,193.15) --
	(129.00,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.00,195.95) --
	(124.23,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (124.23,193.15) --
	(124.23,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (109.13,165.15) --
	(109.13,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (109.13,167.95) --
	(103.61,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (103.61,165.15) --
	(103.61,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.00, 81.14) --
	(126.00, 86.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.00, 83.94) --
	(120.97, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.97, 81.14) --
	(120.97, 86.74);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (102.86,139.95) circle (  3.57);

\path[fill=fillColor] (102.91,447.98) circle (  3.57);

\path[fill=fillColor] ( 97.61,419.98) circle (  3.57);

\path[fill=fillColor] ( 85.98,363.97) circle (  1.43);

\path[fill=fillColor] ( 92.52,335.97) circle (  3.57);

\path[fill=fillColor] ( 93.32,307.96) circle (  3.57);

\path[fill=fillColor] (100.71,111.94) circle (  3.57);

\path[fill=fillColor] (101.68,279.96) circle (  3.57);

\path[fill=fillColor] (109.66,251.96) circle (  3.57);

\path[fill=fillColor] (112.02,223.96) circle (  3.57);

\path[fill=fillColor] (126.59,195.95) circle (  3.57);

\path[fill=fillColor] (106.34,167.95) circle (  3.57);

\path[fill=fillColor] (123.48, 83.94) circle (  3.57);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,153.95) -- (137.25,153.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 78.32,125.95) -- (137.25,125.95);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 78.32, 67.14) rectangle (137.25,464.78);
\end{scope}
\begin{scope}
\path[clip] (142.75, 67.14) rectangle (201.69,464.78);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (142.75, 67.14) rectangle (201.69,464.78);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (152.13, 67.14) --
	(152.13,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (165.53, 67.14) --
	(165.53,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (178.92, 67.14) --
	(178.92,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (192.32, 67.14) --
	(192.32,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75, 83.94) --
	(201.69, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,111.94) --
	(201.69,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,139.95) --
	(201.69,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,167.95) --
	(201.69,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,195.95) --
	(201.69,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,223.96) --
	(201.69,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,251.96) --
	(201.69,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,279.96) --
	(201.69,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,307.96) --
	(201.69,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,335.97) --
	(201.69,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,363.97) --
	(201.69,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,391.97) --
	(201.69,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,419.98) --
	(201.69,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,447.98) --
	(201.69,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.43, 67.14) --
	(145.43,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (158.83, 67.14) --
	(158.83,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.22, 67.14) --
	(172.22,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (185.62, 67.14) --
	(185.62,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (199.01, 67.14) --
	(199.01,464.78);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.63,137.15) --
	(159.63,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.63,139.95) --
	(150.10,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.10,137.15) --
	(150.10,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.33,445.18) --
	(151.33,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.33,447.98) --
	(148.11,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (148.11,445.18) --
	(148.11,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.97,417.18) --
	(157.97,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.97,419.98) --
	(152.24,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.24,417.18) --
	(152.24,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.17,361.17) --
	(154.17,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.72,333.17) --
	(161.72,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.72,335.97) --
	(157.11,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.11,333.17) --
	(157.11,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.19,305.16) --
	(161.19,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.19,307.96) --
	(153.10,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.10,305.16) --
	(153.10,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.52,109.14) --
	(153.52,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.52,111.94) --
	(152.29,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.29,109.14) --
	(152.29,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.70,277.16) --
	(154.70,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.70,279.96) --
	(146.93,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (146.93,277.16) --
	(146.93,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (169.12,249.16) --
	(169.12,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (169.12,251.96) --
	(162.37,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.37,249.16) --
	(162.37,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.04,165.15) --
	(153.04,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.04,167.95) --
	(149.24,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (149.24,165.15) --
	(149.24,170.75);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (154.86,139.95) circle (  3.57);

\path[fill=fillColor] (149.72,447.98) circle (  3.57);

\path[fill=fillColor] (155.13,419.98) circle (  3.57);

\path[fill=fillColor] (149.67,363.97) circle (  1.43);

\path[fill=fillColor] (159.42,335.97) circle (  3.57);

\path[fill=fillColor] (157.17,307.96) circle (  3.57);

\path[fill=fillColor] (152.88,111.94) circle (  3.57);

\path[fill=fillColor] (150.85,279.96) circle (  3.57);

\path[fill=fillColor] (165.74,251.96) circle (  3.57);

\path[fill=fillColor] (151.17,167.95) circle (  3.57);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,153.95) -- (201.69,153.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.75,125.95) -- (201.69,125.95);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (142.75, 67.14) rectangle (201.69,464.78);
\end{scope}
\begin{scope}
\path[clip] (207.19, 67.14) rectangle (266.13,464.78);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (207.19, 67.14) rectangle (266.13,464.78);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (216.57, 67.14) --
	(216.57,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (229.96, 67.14) --
	(229.96,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (243.36, 67.14) --
	(243.36,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (256.76, 67.14) --
	(256.76,464.78);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2021-06-22 11:48:16
% !TEX encoding = UTF-8 Unicode
% !TEX program = xelatex

\documentclass[fontsize=7pt,DIV=calc]{scrartcl}

@@

\usepackage[active,tightpage,xetex]{preview}

\usepackage{fontspec,xunicode}

@@

\setlength\PreviewBorder{0pt}

\setmainfont{Arial}
\begin{document}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (722.70,542.03);
\end{scope}
\begin{scope}
\path[clip] ( 64.26, 25.44) rectangle (124.60,470.61);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 64.26, 25.44) rectangle (124.60,470.61);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 74.80, 25.44) --
	( 74.80,470.61);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 88.25, 25.44) --
	( 88.25,470.61);

\path[draw=drawColor,line width= 0.3pt,line join=round] (101.69, 25.44) --
	(101.69,470.61);

\path[draw=drawColor,line width= 0.3pt,line join=round] (115.14, 25.44) --
	(115.14,470.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26, 44.25) --
	(124.60, 44.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26, 75.60) --
	(124.60, 75.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,106.95) --
	(124.60,106.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,138.30) --
	(124.60,138.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,169.65) --
	(124.60,169.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,201.00) --
	(124.60,201.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,232.35) --
	(124.60,232.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,263.70) --
	(124.60,263.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,295.05) --
	(124.60,295.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,326.40) --
	(124.60,326.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,357.75) --
	(124.60,357.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,389.10) --
	(124.60,389.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,420.45) --
	(124.60,420.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,451.80) --
	(124.60,451.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.08, 25.44) --
	( 68.08,470.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.52, 25.44) --
	( 81.52,470.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.97, 25.44) --
	( 94.97,470.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (108.41, 25.44) --
	(108.41,470.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (121.86, 25.44) --
	(121.86,470.61);
\definecolor{drawColor}{RGB}{204,102,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 98.36,103.81) --
	( 98.36,110.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 98.36,106.95) --
	( 81.68,106.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.68,103.81) --
	( 81.68,110.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 92.98,448.66) --
	( 92.98,454.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 92.98,451.80) --
	( 87.17,451.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.17,448.66) --
	( 87.17,454.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.30,417.31) --
	( 88.30,423.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.30,420.45) --
	( 81.20,420.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.20,417.31) --
	( 81.20,423.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.87,354.61) --
	( 77.87,360.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.87,357.75) --
	( 68.24,357.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 68.24,354.61) --
	( 68.24,360.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.79,323.26) --
	( 81.79,329.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.79,326.40) --
	( 77.49,326.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 77.49,323.26) --
	( 77.49,329.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.64,291.91) --
	( 84.64,298.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 84.64,295.05) --
	( 76.20,295.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 76.20,291.91) --
	( 76.20,298.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.73, 72.46) --
	( 88.73, 78.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 88.73, 75.60) --
	( 87.01, 75.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 87.01, 72.46) --
	( 87.01, 78.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.13,260.56) --
	( 95.13,266.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.13,263.70) --
	( 82.54,263.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 82.54,260.56) --
	( 82.54,266.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.29,229.21) --
	(100.29,235.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.29,232.35) --
	( 93.41,232.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 93.41,229.21) --
	( 93.41,235.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (103.41,197.86) --
	(103.41,204.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (103.41,201.00) --
	( 95.02,201.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.02,197.86) --
	( 95.02,204.13);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.27,166.51) --
	(116.27,172.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.27,169.65) --
	(111.48,169.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.48,166.51) --
	(111.48,172.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.31,135.16) --
	( 96.31,141.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.31,138.30) --
	( 90.77,138.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.77,135.16) --
	( 90.77,141.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.25, 41.12) --
	(113.25, 47.39);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.25, 44.25) --
	(108.20, 44.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (108.20, 41.12) --
	(108.20, 47.39);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] ( 90.02,106.95) circle (  1.96);

\path[fill=fillColor] ( 90.07,451.80) circle (  1.96);

\path[fill=fillColor] ( 84.75,420.45) circle (  1.96);

\path[fill=fillColor] ( 73.08,357.75) circle (  1.96);

\path[fill=fillColor] ( 79.64,326.40) circle (  1.96);

\path[fill=fillColor] ( 80.45,295.05) circle (  1.96);

\path[fill=fillColor] ( 87.87, 75.60) circle (  1.96);

\path[fill=fillColor] ( 88.84,263.70) circle (  1.96);

\path[fill=fillColor] ( 96.85,232.35) circle (  1.96);

\path[fill=fillColor] ( 99.22,201.00) circle (  1.96);

\path[fill=fillColor] (113.85,169.65) circle (  1.96);

\path[fill=fillColor] ( 93.52,138.30) circle (  1.96);

\path[fill=fillColor] (110.73, 44.25) circle (  1.96);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26,122.62) -- (124.60,122.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 64.26, 91.27) -- (124.60, 91.27);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 64.26, 25.44) rectangle (124.60,470.61);
\end{scope}
\begin{scope}
\path[clip] (130.10, 25.44) rectangle (190.45,470.61);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (130.10, 25.44) rectangle (190.45,470.61);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (140.64, 25.44) --
	(140.64,470.61);

\path[draw=drawColor,line width= 0.3pt,line join=round] (154.09, 25.44) --
	(154.09,470.61);

\path[draw=drawColor,line width= 0.3pt,line join=round] (167.54, 25.44) --
	(167.54,470.61);

\path[draw=drawColor,line width= 0.3pt,line join=round] (180.98, 25.44) --
	(180.98,470.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10, 44.25) --
	(190.45, 44.25);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10, 75.60) --
	(190.45, 75.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,106.95) --
	(190.45,106.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,138.30) --
	(190.45,138.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,169.65) --
	(190.45,169.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,201.00) --
	(190.45,201.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,232.35) --
	(190.45,232.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,263.70) --
	(190.45,263.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,295.05) --
	(190.45,295.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,326.40) --
	(190.45,326.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,357.75) --
	(190.45,357.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,389.10) --
	(190.45,389.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,420.45) --
	(190.45,420.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,451.80) --
	(190.45,451.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] (133.92, 25.44) --
	(133.92,470.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (147.37, 25.44) --
	(147.37,470.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (160.81, 25.44) --
	(160.81,470.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (174.26, 25.44) --
	(174.26,470.61);

\path[draw=drawColor,line width= 0.6pt,line join=round] (187.70, 25.44) --
	(187.70,470.61);
\definecolor{drawColor}{RGB}{221,204,119}

\path[draw=drawColor,line width= 0.6pt,line join=round] (148.17,103.81) --
	(148.17,110.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (148.17,106.95) --
	(138.60,106.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (138.60,103.81) --
	(138.60,110.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.84,448.66) --
	(139.84,454.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.84,451.80) --
	(136.61,451.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] (136.61,448.66) --
	(136.61,454.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] (146.51,417.31) --
	(146.51,423.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (146.51,420.45) --
	(140.75,420.45);

\path[draw=drawColor,line width= 0.6pt,line join=round] (140.75,417.31) --
	(140.75,423.58);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.69,354.61) --
	(142.69,360.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.69,357.75) --
	(133.71,357.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (133.71,354.61) --
	(133.71,360.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.27,323.26) --
	(150.27,329.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.27,326.40) --
	(145.65,326.40);

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.65,323.26) --
	(145.65,329.53);

\path[draw=drawColor,line width= 0.6pt,line join=round] (149.73,291.91) --
	(149.73,298.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (149.73,295.05) --
	(141.61,295.05);

\path[draw=drawColor,line width= 0.6pt,line join=round] (141.61,291.91) --
	(141.61,298.18);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.04, 72.46) --
	(142.04, 78.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] (142.04, 75.60) --
	(140.81, 75.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] (140.81, 72.46) --
	(140.81, 78.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.23,260.56) --
	(143.23,266.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (143.23,263.70) --
	(135.43,263.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (135.43,260.56) --
	(135.43,266.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.69,229.21) --
	(157.69,235.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.69,232.35) --
	(150.92,232.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.92,229.21) --
	(150.92,235.48);

\path[draw=drawColor,line width= 0.6pt,line join=round] (141.56,135.16) --
	(141.56,141.43);

\path[draw=drawColor,line width= 0.6pt,line join=round] (141.56,138.30) --
	(137.74,138.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (137.74,135.16) --
	(137.74,141.43);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (143.39,106.95) circle (  1.96);

\path[fill=fillColor] (138.22,451.80) circle (  1.96);

\path[fill=fillColor] (143.66,420.45) circle (  1.96);

\path[fill=fillColor] (138.17,357.75) circle (  1.96);

\path[fill=fillColor] (147.96,326.40) circle (  1.96);

\path[fill=fillColor] (145.70,295.05) circle (  1.96);

\path[fill=fillColor] (141.40, 75.60) circle (  1.96);

\path[fill=fillColor] (139.35,263.70) circle (  1.96);

\path[fill=fillColor] (154.30,232.35) circle (  1.96);

\path[fill=fillColor] (139.68,138.30) circle (  1.96);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10,122.62) -- (190.45,122.62);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.10, 91.27) -- (190.45, 91.27);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (130.10, 25.44) rectangle (190.45,470.61);
\end{scope}
\begin{scope}
\path[clip] (195.95, 25.44) rectangle (256.29,470.61);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (195.95, 25.44) rectangle (256.29,470.61);
\definecolor{drawColor}{gray}{0.92}

\path[draw=drawColor,line width= 0.3pt,line join=round] (206.49, 25.44) --
	(206.49,470.61);
